Preliminary Thesis Defence

### 2014-02-25 presentationPTD.tex
add bitcoin attacks
presentation

\usecolortheme[colortext]{geneva}

@@

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{times}
\usepackage[T1]{fontenc}

@@

% Supervisor:&\footnote{Professor of Economics, The Graduate Institute, Geneva; }\\
% Second Reader:&\footnote{Professor of Economics, The Graduate Institute, Geneva; }

@@

\institute[The Graduate Institute, Geneva] % (optional, but mostly needed)
{
  \inst{1}
  Professor of Economics,\\
  Supervisor
    \and
  \inst{2}
  Professor of Economics,\\
  Second Reader
    \and
  \inst{3}
  PhD Student,\\
  bastiaan.quast@graduateinstitute.ch
    \and
  \inst{4}
  The Graduate Institute, Geneva
}

@@

@@

\begin{frame}{Pensions and Child Growth}{Additional Evidence from South Africa}
using the new data
\end{frame}

\section[Surviving Andersonville]{Replication: Surviving Andersonville}

\begin{frame}{Replication: Surviving Andersonville}
these guys mislabeled everything
\end{frame}

\begin{frame}{Uncertainty and Risk in Currency Attacks}{Knightian Uncertainty in Morris and Shin (1998)}
This paper makes no sense!!
\end{frame}

\section[Bitcoin, Stupid Phones]{Bitcoin and Remittances: Stupid Phone Potential}

\begin{frame}{Bitcoin and Remittances}{Stupid Phone Potential}
stupid phones rock!!
\end{frame}

@@

\begin{frame}{End Notes}
  \begin{itemize}
  \item
    The \alert{first main message} of your talk in one or two lines.
  \item
    The \alert{second main message} of your talk in one or two lines.
  \item
    Perhaps a \alert{third message}, but not more than that.
  \end{itemize}

  % The following outlook is optional.
  \vskip0pt plus.5fill
  \begin{itemize}
  \item
    Outlook
    \begin{itemize}
    \item
      Something you haven't solved.
    \item
      Something else you haven't solved.
    \end{itemize}
  \end{itemize}
\end{frame}

>>>>

\usecolortheme[]{geneva}

@@

\usepackage[english]{babel}
%\usepackage[utf8]{inputenc}
%\usepackage{times}
%\usepackage[T1]{fontenc}
\usepackage[authordate,noibid,backend=biber]{biblatex-chicago}
\usepackage[]{hyperref}

\addbibresource{bibliography.bib}

\setbeamertemplate{bibliography item}{}

@@

@@

\institute[The Graduate Institute, Geneva]
{
  \inst{1}
  Professor of Economics,\\
  Supervisor
    \and
  \inst{2}
  Professor of Economics,\\
  Second Reader
    \and
  \inst{3}
  PhD Student,\\
  bastiaan.quast@graduateinstitute.ch
    \and
  \inst{4}
  The Graduate Institute, Geneva
}

@@

\begin{frame}{Questions}
Cryptocurrency Inflation
	\begin{itemize}
		\item Relevant enough for Development Economics?
	\end{itemize}
Knightian Uncertainty:
	\begin{itemize}
		\item What to do with this critique?
	\end{itemize}
Pensions and  Child Growth:
	\begin{itemize}
		\item Defining of Age-Based and Height-Based Z-scores,\\ correct?
		\item BMI as convex mapping of Weight-for-Height,\\ significance?
		\item Drop in children living with recipient 2008-2012,\\ 		how to account for this?
	\end{itemize}
\end{frame}

\section{Cryptocurrency Inflation}

\begin{frame}{Cryptocurrency Inflation}
Often heard problems Bitcoin:
\begin{enumerate}
	\item There is no inflation
	\item Mining is wasteful
\end{enumerate}
Consider Bitcoin together with other Cryptocurrencies
\begin{itemize}
	\item Expansion in no. of coins, but expansion in no. of currencies
	\item Miners will move to less-mined currencies, leading to less waste
	\item Model as positive currency attack \parencite{obstfeld1986rational,obstfeld1996models}
\end{itemize}

\end{frame}

\begin{frame}{Uncertainty and Risk in Currency Attacks}{Knightian Uncertainty in Morris and Shin (1998)}
A review of \citetitle{morris1998unique} \parencite{morris1998unique}
\begin{itemize}
	\item Based on currency models \textcite{obstfeld1986rational,obstfeld1995logic,obstfeld1996models}
	\item Finds a unique equilibrium when `uncertainy' is added
\end{itemize}
Critiques:
\begin{itemize}
	\item Strange result, does not correspond to reality
	\item The `distortion' changes uncertainty to risk, effectively increasing the body of knowledge
	\item The distortion of perception has a uniform distribution, results do not hold under e.g. Gaussian
	\item Speculator risk profile is redefined:
\end{itemize}
\begin{quotation}
	For the next step,
	consider the strategy profile where every speculator attacks the currency if and only if
	the message $x$ is less than some fixed number $k$.
	\hspace{\stretch{1}}\parencite[p.~592]{morris1998unique}
\end{quotation}
\end{frame}

@@

\begin{frame}{Pensions and Child Growth}{Additional Evidence from South Africa I}
	\begin{itemize}
		\item Based on \citetitle{duflo2003grandmothers} \parencite{duflo2000child,duflo2003grandmothers} methodology
		\item Address the issue of eligibility-age discrepancy
		\item South African Household Survey \parencite{saldru2008nids,saldru2012nids,saldru2013nids}
		\item Elibility-age equalisation in 2009
	\end{itemize}
	Model:
	\setcounter{equation}{2}
	\begin{equation}
		\label{sa:eq:interaction}
		y_{it} = \gamma_i + \lambda_t + \mu P^f_{it} + \nu P^m_{it} + X_{it} + \delta T_{it} + \rho T_{it}*P^m_{it} + \epsilon_{it}
		\end{equation}
\end{frame}

\begin{frame}{Pensions and Child Growth}{Additional Evidence from South Africa II}
	\begin{table}[!ht]
	\centering
	\caption{Height-for-Age Z-score}
	\label{sa:ta:haz}
		\begin{tabular}{l|rrr}
		\hline
		specification & 1 & 2 & 3\\
		\hline
		w\_spen\_m & 0.2366 & *0.8228 & 0.7908 \\
		w\_spen\_w & -0.2331 & 0.1053 & 0.1072 \\
		elig.men.60 & & **-0.3419 & **-0.3465 \\
		w\_spen\_m1:elig.men.60 & & & 0.0446 \\
		w\_h\_tinc & -0.0000 & -0.0000 & -0.0000 \\
		\end{tabular}
	\end{table}
\end{frame}

\begin{frame}{Pensions and Child Growth}{Additional Evidence from South Africa III}
	\begin{table}[!ht]
	\centering
	\caption{Weight-for-Age Z-score}
	\label{sa:ta:waz}
	\begin{tabular}{l|rrr}
		\hline
		specification & 1 & 2 & 3\\
		\hline
		w\_spen\_m & 0.2366 & 0.2981 & 0.4780 \\
		w\_spen\_w & -0.2331 & -0.3112 & -0.3280 \\
		elig.men.60 & & ***-0.3475 & **-0.3243 \\
		w\_spen\_m1:elig.men.60 & & & -0.2545 \\
		w\_h\_tinc & -0.0000 & -0.0000 & -0.0000 \\
		\end{tabular}
	\end{table}
\end{frame}

\begin{frame}{Pensions and Child Growth}{Additional Evidence from South Africa IV}
% LaTeX table created manually
% Fri Dec 27 23:53 2013
\begin{table}[!ht]
\centering
\caption{Weight-for-Height Z-score}
\label{sa:ta:whz}
\begin{tabular}{l|rrr}
\hline
specification & 1 & 2 & 3 \\
\hline
w\_spen\_m &  -0.3532 & -0.3210 & -0.4303 \\
w\_spen\_w & 0.0655 & 0.0371 & 0.0478 \\
elig.men.60 & & -0.1417 & -0.1574 \\
w\_spen\_m1:elig.men.60 & & & 0.1484 \\
\end{tabular}
\end{table}
\begin{table}[!ht]
\centering
\caption{Body-Mass-Index Z-score}
\label{sa:ta:bmiz}
\begin{tabular}{l|rrr}
\hline
specification & 1 & 2 & 3 \\
\hline
w\_spen\_m & *-0.8058 & *-0.7905 & *-1.0226 \\
w\_spen\_w & -0.1592 & -0.1956 & -0.1742 \\
elig.men.60 & & -0.1674 & -0.2049 \\
w\_spen\_m1:elig.men.60 & & & 0.3407 \\
\end{tabular}
\end{table}
\end{frame}

@@

\begin{frame}{End Notes}
Summary
  \begin{itemize}
  \item
    Cryptocurrency Inflation, through multiplicity
  \item
	Currency Attacks: uncertainty vs. risk, redefining risk profile, uniform distribution 
  \item
    Pensions and Child Growth: negative effect
  \end{itemize}

Questions  
	\begin{itemize}
	\item
		Cryptocurrency Inflation: relevant for Development Economics?
	\item
		Knightian Uncertainty: What to do with this critique?
	\item
		Pensions and  Child Growth: Account for drop in no. children?
	\end{itemize}
\end{frame}

\begin{frame}[allowframebreaks]{References}
	\printbibliography
\end{frame}
